Evaluation of Types

### 2020-05-15 evaluation/R/evaluate-type-analysis.Rmd
Create graph for function polymorphism

>>>>

```{r, eval = TRUE, verbose = FALSE}
function_polymorphic_freq <-
union_data %>%
distinct(package_name, function_name, parameter_position, alternative_count) %>%
mutate(polymorphic = ifelse(alternative_count > 1, TRUE, is_polymorphic(alternative_count))) %>%
group_by(package_name, function_name) %>%
summarize(polymorphic_position_count = as.integer(sum(polymorphic))) %>%
ungroup() %>%
group_by(polymorphic_position_count) %>%
summarize(function_count = n()) %>%
ungroup() %>%
arrange(polymorphic_position_count)

function_polymorphic_freq_more_than_three <-
function_polymorphic_freq %>%
filter(polymorphic_position_count > 3) %>%
summarize(polymorphic_position_count = "> 3", function_count = sum(function_count))

function_polymorphic_freq <-
function_polymorphic_freq %>%
filter(polymorphic_position_count <= 3) %>%
rbind(function_polymorphic_freq_more_than_three) %>%
mutate(function_percentage = function_count / total_function_count)

(function_polymorphic_freq %>%
ggplot(aes(polymorphic_position_count, function_percentage)) +
geom_col() +
scale_y_continuous(sec.axis = sec_axis(~ . * total_function_count, labels = count_labels), labels = relative_labels) +
scale_x_discrete(limits=c("> 3", 3, 2, 1, 0)) +
labs(x="Polymorphic Positions", y="Functions") +
coord_flip() +
theme(legend.title = element_blank(), legend.position = "top")) %>%
save_graph("function_polymorphism.pdf")

generate_macro("CountMonomorphicFunctions", 
               function_polymorphic_freq %>% filter(polymorphic_position_count == "0") %>% pull(function_count),
               macro_filename)

generate_macro("PercMonomorphicFunctions", 
               function_polymorphic_freq %>% filter(polymorphic_position_count == "0") %>% pull(function_percentage),
               macro_filename)

generate_macro("CountPolymorphicFunctions", 
               total_function_count - function_polymorphic_freq %>% filter(polymorphic_position_count == "0") %>% pull(function_count),
               macro_filename)

generate_macro("PercPolymorphicFunctions", 
               1.0 - function_polymorphic_freq %>% filter(polymorphic_position_count == "0") %>% pull(function_percentage),
               macro_filename)
```
